---
name: Arthur
surname: Heim
document: 
qualifications: PhD
position: "PhD -- analysis and economic policies"
pronouns: he/they:him/them
#googlescholar: "ALzz0kEAAAAJ"
orcid: '0000-0002-2668-5963'
github: "arthurheim"
address: "Paris, France"
link-citations: TRUE
citecolor: blue
#profilepic: "../img/PSE_a.heimCroped.jpg"
www: arthurheim.github.io/Home/
email: "heimarthur@gmail.com"
bluesky: "heimarthur"
headcolor: "a349a4"
footcolor: "ff0080"
linkcolor: "ff0080"
urlcolor: "0000ff" 
aboutme: "I am an applied economist working on the design and evaluation of public policies to reduce inequalities and poverty in France. My work is mostly based on randomised experiments and microeconometrics for policy evaluation. I also manage a programme turning into a national policy using market designs to assign daycare seats in French municipalities. I am currently working as project manager in the Research Evaluation and Statistics department (DSER) of the French National family allowance fund (Cnaf)."
header-includes:
  \usepackage{fontspec}
  \usepackage{float}
  \usepackage{starfont}
  \usepackage{typicons}
  \usepackage{academicons}
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: TRUE
    latex_engine: "xelatex"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(pacman)
pacman::p_load(
  tidyverse,
  here,
  vitae,
  rsvg,
  kableExtra,
  emojifont,
  fontawesome,
  tibble,
  gglgbtq)

colorsLanguages <- palette_lgbtq("bisexual")
knitr::opts_chunk$set(dev = 'svg')
#rm(list=ls())
```

```{r functions, include=FALSE}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}

# You could have one CSV file for each category of 

# appointments <- read_csv(here("data", "appointments.csv"))
# education <- read_csv(here("data", "education.csv"))
# research <- read_csv(here("data", "research_experience.csv"))
# teaching <- read_csv(here("data", "teaching_supervision.csv"))
# awards <- read_csv(here("data", "awards.csv"))
# leadership <- read_csv(here("data", "leadership.csv"))
# presentations <- read_csv(here("data", "presentations.csv"))
# training <- read_csv(here("data", "training.csv"))
# skills <- read_csv(here("data", "skills_table.csv"))
# tools <- read_csv(here("data", "digital_tools.csv"))

readExcelSheets(here::here("Data", "ArthurHeimCareerDataEn.xlsx"))



#bib <- tempfile(fileext = ".bib")


```

\section{Appointments $\quad$ \faSuitcase}

## Current position

```{r CurJob}
MyJob <- appointments %>%
  filter(current == "yes") %>% as.tibble() %>% 
  detailed_entries(with = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

MyJob
```

## Past experiences

```{r}
otherjob <- appointments %>%
  filter(current != "yes") %>%
  detailed_entries(with = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

otherjob
```



\section{Education $\quad$ \faInstitution }

```{r}
education %>%
  detailed_entries(where = Institution,
                   when = Year,
                   with = Degree,
                   what = Major,
                   why = Details,
                   .protect = FALSE)
```

\newpage
<!-- # Skills -->


\section{Project management}

\subsection{Field experiments}

<!-- ### Completed {-} -->

```{r}
 ResearchProjects %>%
  filter(type %in% c("field experiment")) %>%
  detailed_entries(with = Project,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

```

\subsection{Market design}
<!-- ### Ongoing {-} -->

```{r include=TRUE}
 ResearchProjects %>%
  filter(type %in% c("market design")) %>% 
  detailed_entries(with = Project,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

```

\subsection{Education}


```{r include=TRUE}
 ResearchProjects %>%
  filter(type %in% c("market design","field experiment")==FALSE) %>% 
  detailed_entries(with = Project,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

```


<!-- \section{PhD thesis $\quad$ \faGraduationCap} -->

<!-- ```{r} -->
<!-- Thesis %>% -->
<!--   filter(draftAvailable == "yes") %>% -->
<!--   detailed_entries(what = subtitle, -->
<!--                    when = glue::glue("{status}: {end_date}"), -->
<!--                    with = glue::glue("{title} {link}"), -->
<!--                    where = coauthors, -->
<!--                    why = details, -->
<!--                    .protect = FALSE) -->
<!-- ``` -->



<!-- \newpage -->

<!-- \section{Working papers and ongoing projects $\quad$ \faPencilSquare} -->

<!-- ## Ongoing researches -->

<!-- ```{r} -->
<!-- Thesis %>% -->
<!--   filter(status == "Ongoing") %>% -->
<!--   detailed_entries(what = subtitle, -->
<!--                    when = glue::glue("{status}: {end_date}"), -->
<!--                    with = title, -->
<!--                    where = coauthors, -->
<!--                    why = details, -->
<!--                    .protect = FALSE) -->
<!-- ``` -->



# Expertise, consulting and training

```{r}
expertise <- ScientificExpertise %>%
  filter(current != "yes") %>%
  detailed_entries(with = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

expertise
```






\section{Teaching experiences $\quad$ \faGroup}

```{r}
teaching %>%
  detailed_entries(what = where,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = institution,
                   why = details,
                   .protect = FALSE)
```





\section{Publications $\quad$ \faFolderOpen}

### Academic papers  {-}

##	Early childhood care and education


```{r PubECEC}
PapersECEC <- PaperDetails %>%
  filter(bibtex_ID %in% c("CarbucciaEtAl2024","CombeHeim2024")) %>% as.tibble() %>% 
  detailed_entries(with = title,
                   when = status,
                   what = coauthors,
                   where = glue::glue("{end_date}"),
                   why = details,
                   .protect = FALSE)

PapersECEC
```

<!-- Bibtex version -->
```{r, include=FALSE}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter( id %in% c("CarbucciaEtAl2024", "CombeHeim2024"))

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```

##	Active labour market policies for single parents


```{r PubALMP}
PapersALMP <- PaperDetails %>%
  filter(bibtex_ID %in% c("Heim2024","GalitzineHeim2024")) %>% as.tibble() %>%
  detailed_entries(with = title,
                   when = status,
                   what = coauthors %>% replace_na(.,""),
                   where = glue::glue("{end_date}"),
                   why = details,
                   .protect = FALSE)

PapersALMP
```

<!-- Bibtex version -->
```{r , include=FALSE}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter( id %in% c("Heim2024", "GalitzineHeim2024"))

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```

\clearpage
## Collective work on reproducible research

```{r}
PaperDetails %>%
  filter(bibtex_ID %in% "multi1002024") %>%
  detailed_entries(with = title,
when = status,
what = coauthors %>% replace_na(.,""),
where = glue::glue("{end_date}"),
why = details,
.protect = FALSE)

                   
                   
                   
                   
                   
```





<!-- ## PhD Thesis -->


<!-- ```{r PhDThesis} -->
<!-- PhDThesis <- PaperDetails %>% -->
<!--   filter(bibtex_ID %in% c("Heim2024a")) %>% as.tibble() %>% -->
<!--   detailed_entries(with = title, -->
<!--                    when = status, -->
<!--                    what = coauthors %>% replace_na(.,""), -->
<!--                    where = glue::glue("{end_date}"), -->
<!--                    why = details, -->
<!--                    .protect = FALSE) -->
<!-- PhDThesis -->

<!-- ``` -->

<!-- Thesis --> 



<!-- ```{r include=FALSE} -->
<!-- # did not like this format so will add manually for now -->
<!-- bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>%  -->
<!--   mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt)) -->

<!-- bib %>% filter( id %in% c("Heim2024a")) -->

<!--   #arrange(desc(issued)) -->
<!-- # bibliography_entries(here("data", "papers.bib")) -->
<!-- ``` -->


### Book in French  {-}
<!-- \footnotesize -->
```{r}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter(bib$type=="book")

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```
<!-- \clearpage -->
### Evaluation and policy reports in French  {-}

## Anti poverty policies

```{r}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter( id %in% c("GrobonEtAl2021a", "Heim2020"))

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```



## Social investment


```{r}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter( id %in% c("FougereHeim2019" ,
                          "FougereHeim2019a",
                          "Heim2018",
                          "Heim2017",
                          "Heim2017a"))

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```



##	Education policies


```{r}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter( id %in% c("HeimGalinie2016",
                          "HeimNi2016" ,
                          "MonsEtAl2015",
                          "HeimSteinmetz2015",
                          "HeimSteinmetz2015a",
                          "HeimSteinmetz2015c"
                          ))

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```



<!-- ## Blogging  -->



<!-- ```{r} -->
<!-- # did not like this format so will add manually for now -->
<!-- bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>%  -->
<!--   mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt)) -->

<!-- bib %>% filter( id %in% c("Heim2014", -->
<!--                           "Heim2014a" -->
<!--                           )) -->

<!--   #arrange(desc(issued)) -->
<!-- # bibliography_entries(here("data", "papers.bib")) -->
<!-- ``` -->



<!-- \clearpage -->
\section{Selected conferences $\quad$ \faInstitution}


```{r}
conferences %>%
  detailed_entries(what = institution,
                   when = date,
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```



# Languages 

```{r simpleLang, results='markup'}
# tribble(
#    ~type, ~desc,
#    "Coding Languages",
#     "R -- Python -- SQL -- JavaScript",
#    "Software",
#   "QGIS -- Earth Engine -- SAGA -- PostgreSQL -- ArcGIS -- GIMP",
#    "Other",
#   "Git -- Markdown -- LaTex -- OpenStreetMap"
# ) |>
#   brief_entries(what = desc, with = type, .protect = F)
tribble(
   ~`French`, ~`English`, ~`German`,
  "Native",
  "Proficient",
  "Basic"
) |>
kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") |>
row_spec(0, bold = T, color = "#a349a4") |>
row_spec(1, bold = F, color = "#7f7f7f") |>
column_spec(column = 1:3, width = '4.75cm')
```



```{r langforeign, results='markup', eval=FALSE}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  French = cell_spec(c(rep("Native", 4)), 'latex', color = colorsLanguages[c(1)]), 
  English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = colorsLanguages[c(2)]), 
  German = cell_spec(c("A2","A2","A2","A2"), 'latex', color = colorsLanguages[c(3)]) 
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  ) |>
  column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

<!-- \newpage -->

<!-- \clearpage -->
\section{Programming skills $\quad$ \faConnectdevelop}

<!-- `r fa('r-project', fill = 'steelblue')` -->


```{r include=TRUE}
# skills <- read_csv(here("data", "skills.csv"))
# skills %>%
#   detailed_entries(with = type,
#                    why = skill)
#
library(flextable)
skills %>% 
 
   kbl(booktabs = TRUE, format = "latex",escape = F) %>%
   kable_styling(full_width = F,font_size=10, latex_options = "hold_position",protect_latex=FALSE) %>%
   row_spec(0, bold = T) %>% 
  # row_spec(0, bold = T, color = "#a349a4") |>
#row_spec(1, bold = F, color = "#7f7f7f") |>
column_spec(column = 3, width = '9 cm',color = colorsLanguages[c(3)]) %>% 
column_spec(column = 1, width = '4 cm',bold=T,color = colorsLanguages[c(1)]) %>% 
  column_spec(column = 2,width = '4 cm', italic = T,color = colorsLanguages[c(2)]) 

```


<!-- \clearpage -->

```{r, eval=TRUE,include=FALSE}
#rm(list=ls())
```
