---
name: Arthur
surname: Heim
document: 
qualifications: PhD
position: "PhD -- analysis and economic policies"
pronouns: he/they:him/them
#googlescholar: "ALzz0kEAAAAJ"
orcid: '0000-0002-2668-5963'
github: "arthurheim"
address: "Paris, France"
link-citations: true
citecolor: blue
#profilepic: "../img/PSE_a.heimCroped.jpg"
www: arthurheim.github.io/Home/
email: "heimarthur@gmail.com"
twitter: heimarthur
headcolor: "a349a4"
footcolor: "ff0080"
linkcolor: "ff0080"
urlcolor: "0000ff" 
aboutme: "I am an applied economist working on the design and evaluation of public policies to reduce inequalities and poverty in France. I combine field experiments and microeconometrics to study the effects of active labour market policies for single mothers and how administrative support and information can improve access to early childcare services. I also use market design and implement fair assignment mechanisms for daycare seats in French municipalities.
I am currently working as project manager in the Research Evaluation and Statistics department (DSER) of the French National family allowance fund (Cnaf)."
header-includes:
  \usepackage{fontspec}
  \usepackage{float}
  \usepackage{starfont}
  \usepackage{typicons}
  \usepackage{academicons}
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
    latex_engine: "xelatex"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(pacman)
pacman::p_load(
  tidyverse,
  here,
  vitae,
  rsvg,
  kableExtra,
  emojifont,
  fontawesome,
  tibble,
  gglgbtq)

colorsLanguages <- palette_lgbtq("bisexual")
knitr::opts_chunk$set(dev = 'svg')

```

```{r functions, include=FALSE}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}
# appointments <- read_csv(here("data", "appointments.csv"))
# education <- read_csv(here("data", "education.csv"))
# research <- read_csv(here("data", "research_experience.csv"))
# teaching <- read_csv(here("data", "teaching_supervision.csv"))
# awards <- read_csv(here("data", "awards.csv"))
# leadership <- read_csv(here("data", "leadership.csv"))
# presentations <- read_csv(here("data", "presentations.csv"))
# training <- read_csv(here("data", "training.csv"))
# skills <- read_csv(here("data", "skills_table.csv"))
# tools <- read_csv(here("data", "digital_tools.csv"))

readExcelSheets(here::here("Data", "ArthurHeimCareerDataEn.xlsx"))



#bib <- tempfile(fileext = ".bib")


```

\section{Appointments $\quad$ \faSuitcase}

## Current position

```{r CurJob}
MyJob <- appointments %>%
  filter(current == "yes") %>% as.tibble() %>% 
  detailed_entries(with = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

MyJob
```

## Past experiences

```{r}
otherjob <- appointments %>%
  filter(current != "yes") %>%
  detailed_entries(with = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

otherjob
```


<!-- ## Expertise, consulting and training -->

<!-- ```{r} -->
<!-- expertise <- ScientificExpertise %>% -->
<!--   filter(current != "yes") %>% -->
<!--   detailed_entries(with = role, -->
<!--                    when = glue::glue("{start_date}--{end_date}"), -->
<!--                    what = institution, -->
<!--                    where = where, -->
<!--                    why = details, -->
<!--                    .protect = FALSE) -->

<!-- expertise -->
<!-- ``` -->


\section{Education $\quad$ \faInstitution }

```{r}
education %>%
  detailed_entries(where = Institution,
                   when = Year,
                   with = Degree,
                   what = Major,
                   why = Details,
                   .protect = FALSE)
```

\newpage
<!-- # Skills -->


\section{Teaching experiences $\quad$ \faGroup}

```{r}
teaching %>%
  detailed_entries(what = institution,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```


\section{Programming skills $\quad$ \faConnectdevelop}

<!-- `r fa('r-project', fill = 'steelblue')` -->


```{r include=TRUE}
# skills <- read_csv(here("data", "skills.csv"))
# skills %>%
#   detailed_entries(with = type,
#                    why = skill)
#
library(flextable)
skills %>% 
 
   kbl(booktabs = TRUE, format = "latex",escape = F) %>%
   kable_styling(full_width = F,font_size=10, latex_options = "hold_position",protect_latex=FALSE) %>%
   row_spec(0, bold = T) %>% 
  # row_spec(0, bold = T, color = "#a349a4") |>
#row_spec(1, bold = F, color = "#7f7f7f") |>
column_spec(column = 3, width = '9 cm',color = colorsLanguages[c(3)]) %>% 
column_spec(column = 1, width = '4 cm',bold=T,color = colorsLanguages[c(1)]) %>% 
  column_spec(column = 2,width = '4 cm', italic = T,color = colorsLanguages[c(2)]) 

```


\section{Research projects}

\subsection{PhD Thesis}
```{r}
 ResearchProjects %>%
  filter(include == "PhD") %>%
  detailed_entries(with = Project,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

```


\subsection{Ongoing research projects}
```{r}
 ResearchProjects %>%
  filter(include != "PhD") %>%
  detailed_entries(with = Project,
                   when = glue::glue("{start_date}--{end_date}"),
                   what = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)

```



<!-- \section{PhD thesis $\quad$ \faGraduationCap} -->

<!-- ```{r} -->
<!-- Thesis %>% -->
<!--   filter(draftAvailable == "yes") %>% -->
<!--   detailed_entries(what = subtitle, -->
<!--                    when = glue::glue("{status}: {end_date}"), -->
<!--                    with = glue::glue("{title} {link}"), -->
<!--                    where = coauthors, -->
<!--                    why = details, -->
<!--                    .protect = FALSE) -->
<!-- ``` -->



<!-- \newpage -->

\section{Working papers and ongoing projects $\quad$ \faPencilSquare}

## Ongoing researches

```{r}
Thesis %>%
  filter(status == "Ongoing") %>%
  detailed_entries(what = subtitle,
                   when = glue::glue("{status}: {end_date}"),
                   with = title,
                   where = coauthors,
                   why = details,
                   .protect = FALSE)
```


## Collective work on reproducible research

```{r}
Thesis %>%
  filter(status == "Collective") %>%
  detailed_entries(what = subtitle,
                   when = glue::glue("{status}: {end_date}"),
                   with = title,
                   where = coauthors,
                   why = details,
                   .protect = FALSE)
```



\section{Publications $\quad$ \faFolderOpen}


## Book
<!-- \footnotesize -->
```{r}
# did not like this format so will add manually for now
bib <- bibliography_entries(here("Data", "publi_heim2.bib"))%>%distinct(title,.keep_all = TRUE) %>% 
  mutate(dt=as.numeric(str_remove_all(id,"[:alpha:]"))) %>% arrange(desc(dt))

bib %>% filter(bib$type=="book")

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```


## Pre-doctoral and policy work
<!-- \footnotesize -->
```{r}


bib %>% filter(dt<2023 & (type %in% c("webpage",'book')==FALSE) & str_detect(bib$id,"ontaignac")==FALSE)

  #arrange(desc(issued))
# bibliography_entries(here("data", "papers.bib"))
```

<!-- \clearpage -->
\section{Selected conferences $\quad$ \faInstitution}


```{r}
conferences %>%
  detailed_entries(what = institution,
                   when = date,
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```



# Languages 

```{r simpleLang, results='markup'}
# tribble(
#    ~type, ~desc,
#    "Coding Languages",
#     "R -- Python -- SQL -- JavaScript",
#    "Software",
#   "QGIS -- Earth Engine -- SAGA -- PostgreSQL -- ArcGIS -- GIMP",
#    "Other",
#   "Git -- Markdown -- LaTex -- OpenStreetMap"
# ) |>
#   brief_entries(what = desc, with = type, .protect = F)
tribble(
   ~`French`, ~`English`, ~`German`,
  "Native",
  "Proficient",
  "Basic"
) |>
kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") |>
row_spec(0, bold = T, color = "#a349a4") |>
row_spec(1, bold = F, color = "#7f7f7f") |>
column_spec(column = 1:3, width = '4.75cm')
```



```{r langforeign, results='markup', eval=FALSE}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  French = cell_spec(c(rep("Native", 4)), 'latex', color = colorsLanguages[c(1)]), 
  English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = colorsLanguages[c(2)]), 
  German = cell_spec(c("A2","A2","A2","A2"), 'latex', color = colorsLanguages[c(3)]) 
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  ) |>
  column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```



<!-- \clearpage -->

```{r, eval=TRUE,include=FALSE}
rm(list=ls())
```
